A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2015-09-14 docs/results_photometry_v1.01.tex
Wrote section on future work and removed some TO DOs.

\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{fig/1331F814Wsci_MGE_M.ps}
\caption{MGE for J1331's inner regions: Comparison of contours with constant F814W surface brightness of J1331's central region (orange lines) with the corresponding iso-brightness contours of the best fit MGE in Table \ref{tab:MGEF814W}, convolved with the PSF in Table \ref{tab:MGEF814W}, (gray lines). The MGE model is a good representation of the galaxy's light distribution within $\sim 5$ arcsec. Image scaling and orientation are indicated in the figure. The black line has a length of 10 arcsec and it's orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}. For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed line. This MGE is used in the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}. [TO DO: explain how this MGE is used in dynamical modelling]}
\label{fig:MGEinnerRegions}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
\caption{MGE for J1331's outer regions: Comparison of contours with constant surface brightness of the smooth IRAF ELLIPSE model for J1331 in the F814W filter (yellow) with a corresponding best fit MGE (gray lines). The green box corresponds to the image section shown in Figure \ref{fig:MGEinnerRegions}, with the Einstein radius as dashed red line. [TO DO: caption]}
\label{fig:MGEouterRegions}
\end{figure}

@@

\begin{table}
\centering
\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Equation \ref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image by [TO DO].}
\begin{tabular}{ccc}
\hline
$k$ & $G_k$ & $\delta_k$ [arcsec] \\\hline
1 & 0.184 & 0.038\\
2 & 0.485 & 0.085\\
3 & 0.222 & 0.169\\
4 & 0.109 & 0.487\\\hline
\end{tabular}
\label{tab:PSFMGEF814W}
\end{table}

@@

\begin{table*}
\centering
\caption{Galaxy Parameters of J1331}
\begin{tabular}{lllrl}
\hline
redshift                  & $z_d$ & 0.113 & \citep{SWELLSIII}\\
angular diameter distance & $D_d$ [Mpc] & 414 & \\
scaling                   & 1 kpc / 1 arcsec & 2.006 & \\
position angle            & $\phi$ [degrees] & wrt what???\\
average axis ratio & $q'$ & 0.598\\
average ellipticity & $\epsilon = 1 - q'$ & 0.402 & \\
apparent I-band magnitude & $m_\text{I}$ [mag] & 15.77 & \\
total I-band luminosity & $L_\text{tot,I}$ [$10^{10} L_\odot$] & 5.6 & \\
effective half-light radius & $R_\text{eff}$ [arcsec] & 2.6 & \\
& $R_\text{eff}$ [pc]& 5.2 & \\
\hline
\end{tabular}
\label{tab:galaxyparameters}
\end{table*}

@@

\paragraph{PSF for the HST/F814W filter.} We find a radial profile for the HST/F814W filter PSF from circular annuli within a synthetic PSF image from [TO DO: Where did we get this image from???], ignoring diffraction spikes. The one-dimensional MGE fit of Equation \ref{eq:PSFgeneral} to this radial profile is performed using the code by [TO DO: REF and footnote to code]. The MGE parameters of the normalized PSF model are given in Table \ref{tab:PSFMGEF814W}.

@@

\paragraph{Transformation into physical units.} To transform the MGE in units of counts into physical units, we apply a simplified version of the procedure described in \citet{Holtzman}, analogous to [TO DO: Cappellari Read me file???]
\\The scaling of the drizzled HST/WFC3 images is  $S = 0.05$ arcsec/pixel and the total exposure time $T = 1600$ sec. The total F814W luminosity in counts of each Gaussian of the MGE has a central surface brightness in counts per pixel of
\begin{equation*}
C_0\text{[counts/pixel]} = \frac{L[\text{counts}]}{2\pi \sigma[\text{pixel}]^2 q}.
\end{equation*}
This is then transformed into an I-band surface brightness via
\begin{equation}
\mu_I \simeq -2.5 \log_{10}\left( \frac{C_0\text{[counts/pixel]}}{T[\text{sec}] \cdot S[\text{arcsec/pixel}]^2}\right) + Z + C + A_I, \label{eq:muI_}
\end{equation}
where $Z\simeq21.62$ is a the zero-point from \citet{Holtzman}  (updated according to \citet{Dolphin,DolphinNew}) for the photometric system of the HST/WFPC2 camera and the F814W filter plus a correction for the difference in gain between calibration and observation. $C= 0.1$ corrects for the finite aperture of the WFPC2. And $A_I =0.015$ mag  is the extinction in the I-band tpwards J1331, according to the NASA/IPAC Extragalactic Database [TO DO: proper reference]. The color-dependent correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore. The last step is to transform the surface brightness $\mu_i$ in mag to the I-band surface density of the Gaussian in $L_\odot$/pc$^2$ as
\begin{eqnarray*}
I_0[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z \right)^4 10^{0.4\left(M_{\odot,I}-\mu_I \right)},
\end{eqnarray*}
where the term with $z$ accounts for redshift dimming and $M_{\odot,I}=4.08$ mag is the sun's absolute I-band magnitude \citep{1998gaas.book.....B}. The luminosity $L_k$[counts] and the corresponding surface brightness density $I \equiv I_{0,k}[L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{fig:MGEinnerRegions}. [TO DO: I'm really confused about this. Check, that everything is correct and the naming of quantities, e.g. with or without subscripts of 0, is fine???] [TO DO: Maybe shift to appendix???]

\paragraph{Inclination.} To estimate the inclination of J1331 with respect to the observer, we use the observed axis ratio of the flattest ellipse in the Iraf Ellipse [TO DO] model for J1331, which is $q'=0.42$. This is similar to the disk axis ratio of $q' = 0.40$ found by \citet{SWELLSI} [TO DO: CHECK]. If a typical thickness of an oblate disk was around $q_0 \sim 0.2$ [TO DO: REF: Holmberg 1985], the inclination would follow from $\cos^2 i = \frac{q'^2 - q_0^2}{1 - q_0^2}$ and a correction of $+3^\circ$ [TO DO: REF: Tully 1988]. Our estimate for the inclination is therefore $i \approx 70^\circ$.

>>>>

\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{fig/1331F814Wsci_MGE_M.ps}
\caption{MGE for J1331's inner regions: Comparison of contours with constant F814W surface brightness of J1331's central region (orange lines) with the corresponding iso-brightness contours of the best fit MGE in Table \ref{tab:MGEF814W}, convolved with the PSF in Table \ref{tab:MGEF814W}, (gray lines). The MGE model is a good representation of the galaxy's light distribution along the major axis within $\sim 5$ arcsec. Image scaling and orientation are indicated in the figure. The black line has a length of 10 arcsec and it's orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}. For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed line. This MGE is used as model for the stellar tracer distribution in the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.}
\label{fig:MGEinnerRegions}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
\caption{MGE for J1331's outer regions: Comparison of contours with constant surface brightness of the smooth IRAF ELLIPSE [TO DO: How to write Iraf Ellipse???] model for J1331 in the F814W filter (yellow) with a corresponding best fit MGE (gray lines). The green box corresponds to the image section shown in Figure \ref{fig:MGEinnerRegions}, with the Einstein radius as dashed red line and the black 10 arcsec orientation line along the major axis (see Figure \ref{fig:MGEinnerRegions}). This MGE found from the smooth, symmetric Iraf Ellipse [TO DO] model is not used to find a dynamical model for J1331, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g. spiral arms). We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions by extrapolation the best fit model of the inner regions.}
\label{fig:MGEouterRegions}
\end{figure}

@@

\begin{table}
\centering
\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Equation \ref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image by [TO DO: WHO???].}
\begin{tabular}{ccc}
\hline
$k$ & $G_k$ & $\delta_k$ [arcsec] \\\hline
1 & 0.184 & 0.038\\
2 & 0.485 & 0.085\\
3 & 0.222 & 0.169\\
4 & 0.109 & 0.487\\\hline
\end{tabular}
\label{tab:PSFMGEF814W}
\end{table}

@@

\begin{table*}
\centering
\caption{Galaxy Parameters of J1331}
\begin{tabular}{lllrl}
\hline
redshift                  & $z_d$ & 0.113 & \citep{SWELLSIII}\\
angular diameter distance & $D_d$ [Mpc] & 414 & \\
scaling                   & 1 kpc / 1 arcsec & 2.006 & \\
position angle            & $\phi$ [degrees] & [TO DO: wrt what???]\\
average axis ratio & $q'$ & 0.598\\
average ellipticity & $\epsilon = 1 - q'$ & 0.402 & \\
apparent I-band magnitude & $m_\text{I}$ [mag] & 15.77 & \\
total I-band luminosity & $L_\text{tot,I}$ [$10^{10} L_\odot$] & 5.6 & \\
effective half-light radius & $R_\text{eff}$ [arcsec] & 2.6 & \\
& $R_\text{eff}$ [pc]& 5.2 & \\
\hline
\end{tabular}
\label{tab:galaxyparameters}
\end{table*}

@@

\paragraph{PSF for the HST/F814W filter.} We find a radial profile for the HST/F814W filter PSF from circular annuli within a synthetic PSF image from [TO DO: Where did we get this image from???], ignoring diffraction spikes. The one-dimensional MGE fit of Equation \ref{eq:PSFgeneral} to this radial profile is performed using the code by \citet{Cap02}. The MGE parameters of the normalized PSF model are given in Table \ref{tab:PSFMGEF814W}.

@@

\paragraph{Transformation into physical units.} To transform the MGE in units of counts into physical units, we apply a simplified version of the procedure described in \citet{Holtzman}, analogous to [TO DO: Cappellari Read me file??? How to reference this???]
\\The scaling of the drizzled HST/WFC3 images is  $S = 0.05$ arcsec/pixel and the total exposure time $T = 1600$ sec. The total F814W luminosity in counts of each Gaussian of the MGE has a central surface brightness in counts per pixel of
\begin{equation*}
C_0\text{[counts/pixel]} = \frac{L[\text{counts}]}{2\pi \sigma[\text{pixel}]^2 q}.
\end{equation*}
This is then transformed into an I-band surface brightness via
\begin{equation}
\mu_I \simeq -2.5 \log_{10}\left( \frac{C_0\text{[counts/pixel]}}{T[\text{sec}] \cdot S[\text{arcsec/pixel}]^2}\right) + Z + C + A_I, \label{eq:muI_}
\end{equation}
where $Z\simeq21.62$ is a the zero-point from \citet{Holtzman}  (updated according to \citet{Dolphin,DolphinNew}) for the photometric system of the HST/WFPC2 camera and the F814W filter plus a correction for the difference in gain between calibration and observation. $C= 0.1$ corrects for the finite aperture of the WFPC2. And $A_I =0.015$ mag  is the extinction in the (Landolt) I-band towards J1331, according to the NASA/IPAC Extragalactic Database (NED)\footnote{The NASA/IPAC Extragalactic Database (NED, \url{https://ned.ipac.caltech.edu/}) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration. The data for J1331 (SDSS J133140.33+362811.9) was retrieved in October 2013.}. The color-dependent correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore. The last step is to transform the surface brightness $\mu_i$ in mag to the I-band surface density of the Gaussian in $L_\odot$/pc$^2$ as
\begin{eqnarray*}
I_0[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z \right)^4 10^{0.4\left(M_{\odot,I}-\mu_I \right)},
\end{eqnarray*}
where the term with $z$ accounts for redshift dimming and $M_{\odot,I}=4.08$ mag is the sun's absolute I-band magnitude \citep{1998gaas.book.....B}. The luminosity $L_k$[counts] and the corresponding surface brightness density $I \equiv I_{0,k}[L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{fig:MGEinnerRegions}. [TO DO: I'm really confused about this. Check, that everything is correct and the naming of quantities, e.g. with or without subscripts of 0, is fine???] [TO DO: Maybe shift to appendix or theory part???]

\paragraph{Inclination.} To estimate the inclination of J1331 with respect to the observer, we use the observed axis ratio of the flattest ellipse in the Iraf Ellipse [TO DO] model for J1331, which is $q'=0.42$. This is similar to the disk axis ratio of $q' = 0.40$ found by \citet{SWELLSI}. If a typical thickness of an oblate disk was around $q_0 \sim 0.2$ \citep{1958MeLu2.136....1H}, the inclination would follow from $\cos^2 i = \frac{q'^2 - q_0^2}{1 - q_0^2}$ and a correction of $+3^\circ$ \citep{1988ngc..book.....T}. Our estimate for the inclination is therefore $i \approx 70^\circ$. Given this inclination, the 2D MGE models can be deprojected into three dimensions (see Section \ref{sec:MGE_theo}).
